Comprehensive Quality-Aware Automated Semantic Web Service Composition

### 2017-01-25 paper.tex
up

\begin{document}
\maketitle
\begin{abstract}
Semantic web service composition has been a prevailing research area in recent years. There are two major governance challenges faced by researchers (semantic matching and QoS optimisation). Semantic matchmaking aims to discover interoperable web services that can interact with each other to provide rich functionalities through language understanding and reasoning. QoS optimisation aims to meet non-functional requirement of service users. e.g minimum cost, maximal reliability. Many scholars have looked into nonfunctional optimisation problems in QoS-aware web service composition applying AI planning and Evolution Computing techniques. To meet users' requirement, one often needs to consider both semantic matching and QoS optimisation simultaneously. Existing works on web service composition often concerns either semantic service composition or QoS-aware service composition. However, there are very few works concerns both quality of semantic matchmaking and quality of services at the same time. Therefore, In this paper we consider two quality dimensions in a proposed more applicable comprehensive quality model for semantic web service composition, and present a automated semantic web service composition approach that can generate service composition solutions that meet both functional and non-functional requirement. We will evaluate our approach utilising a semantic benchmark dataset.

@@

Existing works on service composition focus mainly on addressing the one of challenges above. A lot of works have been conducted to optimise the quality of compositions under a pre-defined abstract workflow, which is generally considered as \textit{semi-automated Web service composition} approach. Meanwhile, many research works consider the possibility of generating a composite plan automatically in discovering and selecting suitable web services, which are deemed to NP-hard \cite{moghaddam2014service}. \textit{Semantic web services composition} is distinguished from the syntactic service composition, with the hope of eliminating conflicts by the semantic level of web services. In the past few years, substantial works have been done on semantic web service composition \cite{fensel2011semantic,lecue2009optimizing}. However, few works have enabled truely automatic semantic web service composition, where both QoS and quality of semantic match making will be optimised simultaneously. To a given service request, the quality of service composition solution depends on both QoS and quality of semantic matchmaking. Therefore, a comprehensive quality model is needed to measure the quality of service composition solution.

@@

 \item To evaluate the performance of comprehensive quality awareness semantic web service composition by utilising benchmark datasets from Web Services Challenge 2009 (WSC09) \cite{kona2009wsc}.
\end{enumerate}

@@

\textbf{QoS-aware EC approaches}. Evolution Computing techniques are widely used to solve optimisation problems, where the search space is big, so that near-optimised solutions can be found in reasonable time. Genetic Programming (GP) \cite{da2016particle,da2015graphevol} is a typical EC technique applied to automated web service composition. GP-based approaches utilise tree representations, on which service and constructs are represented as terminal nodes and functional nodes respectively. The crossover and mutation operations reproduce various individuals while ensuring the correctness of structure. In \cite{yu2013adaptive}, the author optimises the overall quality of service composition by using a fitness function, which is also liable for the correctness in functionality through penalising infeasible solutions. Also, this paper increase the mutation rate while encountering low diversity in the population and adopt a higher crossover probability while trapped in local optimisation.

>>>>

\begin{document}
\maketitle
\begin{abstract}
Semantic web service composition has been a prevailing research area in recent years. There are two major governance challenges faced by researchers (semantic matching and QoS optimisation). Semantic matchmaking aims to discover interoperable web services that can interact with each other to provide rich functionalities through language understanding and reasoning. QoS optimisation aims to meet non-functional requirement of service users. e.g minimum cost, maximal reliability. Many scholars have looked into nonfunctional optimisation problems in QoS-aware web service composition applying AI planning and Evolutionary Computation techniques. To meet users' requirement, one often needs to consider both semantic matching and QoS optimisation simultaneously. Existing works on web service composition often concerns either semantic service composition or QoS-aware service composition. However, there are very few works concerns both quality of semantic matchmaking and quality of services at the same time. Therefore, In this paper we consider two quality dimensions in a proposed more applicable comprehensive quality model for semantic web service composition, and present a automated semantic web service composition approach that can generate service composition solutions that meet both functional and non-functional requirement. We will evaluate our approach utilising a semantic benchmark dataset.

@@

Existing works on service composition focus mainly on addressing the one of challenges above. A lot of works have been conducted to optimise the quality of compositions under a pre-defined abstract workflow, which is generally considered as \textit{semi-automated Web service composition} approach. Meanwhile, many research works consider the possibility of generating a composite plan automatically in discovering and selecting suitable web services, which are considered to be NP-hard \cite{moghaddam2014service}. \textit{Semantic web services composition} is distinguished from the syntactic service composition, with the hope of eliminating conflicts by the semantic level of web services. In the past few years, substantial works have been done on semantic web service composition \cite{fensel2011semantic,lecue2009optimizing}. However, few works have enabled truely automatic semantic web service composition, where both QoS and quality of semantic match making will be optimised simultaneously. To a given service request, the quality of service composition solution depends on both QoS and quality of semantic matchmaking. Therefore, a comprehensive quality model is needed to measure the quality of service composition solution.

@@

 \item To evaluate the performance of comprehensive quality awareness semantic web service composition by utilising benchmark datasets from Web Services Challenge 2009 (WSC09) \cite{kona2009wsc}. Also, we make a comparison between PSO-based and an existing GP-based approach employing our proposed comprehensive quality model.

\end{enumerate}

@@

\textbf{QoS-aware EC approaches}. Evolutionary Computation techniques are widely used to solve optimisation problems, where the search space is big, so that near-optimised solutions can be found in reasonable time. Genetic Programming (GP) \cite{da2016particle,da2015graphevol} is a typical EC technique applied to automated web service composition. GP-based approaches utilise tree representations, on which service and constructs are represented as terminal nodes and functional nodes respectively. The crossover and mutation operations reproduce various individuals while ensuring the correctness of structure. In \cite{yu2013adaptive}, the author optimises the overall quality of service composition by using a fitness function, which is also liable for the correctness in functionality through penalising infeasible solutions. Also, this paper increase the mutation rate while encountering low diversity in the population and adopt a higher crossover probability while trapped in local optimisation.
